Verifying Demonstrations

### 2017-10-04 protocol.tex
Adds how to propagate protest ID (fixes #40)

We will start with the latter.
The identifier of the protest must be regulated, for the same reasons as for the 
user identifiers --- otherwise a counter-protest can simply choose the same 
protest identifier.
As was pointed out in \cref{CauseIsTheCommonDenominator}, the cause is at the 
root of what defines a protest.
The cause can be captured in some sort of \enquote{manifesto}, thus, we will use 
the hash value of the manifesto as identifier of the protest.
(As shown as manifesto and \(id\) in \cref{ProofFig}.)

\Textcite{HowToWinTheCloneWars} created an \emph{interactive} credential system 
which allows anonymous authentication at most \(n\) times\footnote{%
  Possibly there is another scheme that makes it non-interactive, e.g.\ by 
  \Textcite{Psignatures}, see issue \#27.
}.
Alice has a \ac{PRF} key \(k\) and a blind signature on \(k\) included in her 
national identity-card (by assumption).
She will use \(k\) to compute \(pid\gets PRF_k(id)\), which is her anonymous 
identity during the protest.
She must also provide \iac{NIZK} proof that \(pid = PRF_k(id)\) and that she 
knows a signature by the identity authority on \(k\).
Thus \(pid\) will be used as the unique identifier in the proof shares and the 
\ac{NIZK} proof will prove the eligibility of \(pid\).

>>>>

We will start with the latter.
The identifier of the protest must be regulated, for the same reasons as for the 
user identifiers --- otherwise a counter-protest can simply choose the same 
protest identifier.
As was pointed out in \cref{CauseIsTheCommonDenominator}, the cause is at the 
root of what defines a protest.
The cause can be captured in some sort of \enquote{manifesto}, thus, we will use 
the hash value of the manifesto as identifier of the protest (cause).
(As shown as manifesto and cause identifier \(cid\) in \cref{ProofFig}.)

To practically propagate this identifier to the protesters the organizer can 
have a placard with a large QR code that either contains the entire manifesto or 
at least links to a website hosting the manifesto.
The user can scan this QR code with a protesting app which will automatically 
fetch it, show it to the protester for approval and then compute the identifier 
\(cid\).

Next we need to consider the protesters' identifiers to prevent Sybil attacks.
\Textcite{HowToWinTheCloneWars} created an \emph{interactive} credential system 
which allows anonymous authentication at most \(n\) times\footnote{%
  Possibly there is another scheme that makes it non-interactive, e.g.\ by 
  \Textcite{Psignatures}, see issue \#27.
}.
Alice has a \ac{PRF} key \(k\) and a blind signature on \(k\) included in her 
national identity-card (by assumption).
She will use \(k\) to compute \(pid\gets PRF_k(id)\), which is her anonymous 
identity during the protest.
She must also provide \iac{NIZK} proof that \(pid = PRF_k(id)\) and that she 
knows a signature by the identity authority on \(k\).
Thus \(pid\) will be used as the unique identifier in the proof shares and the 
\ac{NIZK} proof will prove the eligibility of \(pid\).
